\chapter{Conclusions and Future Work}

\section{Conclusion}
The corruption is increasing day by day. People don’t know who to trust. Every other person in your neighborhood can be working for another person. Building a network topology of people or group of people called mafia is threatening the peace keepers and well-wishers of the society. The best people of society don’t know who to trust. From a simple staff employee to the highest level of the Government Official can be involved in this. The whistle blowers that are reporting or planning on reporting don’t even know who they are talking to. The crime rate in Pakistan is increasing day by day. They are afraid of getting themselves killed or hurt.\\
The Solution to report crime or any illegal activity happening in the country safely is that we develop a blockchain based reward system for whistle blowers where the identities of the Police Officer and the whistle blowers kept safely.\\
The Basic Structure of the application is discussed below:\\
\textbf{The Smart Contract  }-An electronic contract in the blockchain application where the trade is happening when whistle blower reports something and gets rewarded.\\ 
\textbf{The Police }-Will submit both cases and evidence against any case uploaded by any whistle blower or any other police officer. Can view both cases and evidence of any region in the country.\\
\textbf{The People  }-The people will see all the cases up and running currently. If you have anything against any case you have to register on a whistle blower page. \\
\textbf{The Whistle-Blower  }-– Instead of real name or anything they will register through a wallet number. Keeping them unknown to the police and everyone on the system. They can submit both the cases and the evidence against any case.\\
\textbf{The Agency/Judge  }-– They will keep an eye on the cases and officer assigned to that case. Reward them both the officer and the whistle blower for successful closing of the case.\\
The Solution aims to build as many use cases as possible regarding this application. Ensuring the safety of whistle blowers is our first priority. That’s why we used their wallets number to register them instead of their names. The cases older than 3 months will get dispose into another forum.\\ 
Make this prototype as a working model as soon as possible and to get hold and reduce crime rate happening in our country is our main goal. Thanks to our Government and President enthusiasm to take action against crime and involving technology for the safety of good people in our society means a lot to us.  
