\documentclass{fast-nuces-bs}

\usepackage{blindtext}
\usepackage{mathptmx}% Times Roman font
\usepackage[T1]{fontenc}
\usepackage{lipsum} 
\usepackage{sectsty}
\usepackage{tikz-uml}
\usepackage{titlesec}
\usepackage{refstyle}
\usepackage{booktabs} 
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{color, colortbl}
\definecolor{Gray}{gray}{0.9}
% Information about the Thesis 
% -----------------------------------------------------------------------------
% (All are compulsory, do not delete any line other than author Information)
% For e.g., usually there are 3 students in a group, so leave authorone, 
% authortwo, and authorthree, and delete authorfour.
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\department{Department of Computer Science}
\faculty{Computer Science}
\degreeyear{2018}
\degreemonth{December}
\degreename{Computer Science}
\campuscity{Peshawar}
\authortwo{Muhammad Arslan}{P15-6085}
\authorthree{Abdul Moiz Rana}{P15-6091}
\authorone{Muhammad Nafeel Rasheed}{P15-6010}
\supervisor{Dr. Mohammad Nauman}
\sessionduration{2015-2019}

\deanname{Dr. Hasina Khatoon}
\directorname{Dr. Tariq Khan}
\hodname{Dr. Omar Usman Khan}
\fypcoordinatorname{Shakir Ullah}
\title{A Blockchain Based Web Portal For Whistle-Blower Against Illegal Activities}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Former document starts below this
\begin{document}

\begin{acknowledgements}
	We might want to express our most profound gratefulness to every one of the individuals who gave us the likelihood to finish the Final Year Project I. An extraordinary appreciation we provide for our Final year project supervisor,  Dr. Mohammad Nauman whose commitment in animating recommendations and consolation, helped us to facilitate what's more, whose have put his full endeavours in controlling our group in accomplishing the objective which is our venture. 
	
	Moreover we might likewise want to recognize with much thankfulness the vital job 
	of the Head of Department Computer Sciences Dr. Omar Usman Khan, who gave the all 
	required and the fundamental recommendations, inspiration and support to finish the 
	undertaking  \emph{"A Blockchain Based Web Portal For Whistle-Blower Against Illegal Activities"}. We need to welcome the direction given by Evaluators, different chiefs and in addition the entire board particularly in our venture introduction that has enhanced our introduction aptitudes on account of their remark furthermore, advices. We might likewise want to extend our most profound appreciation to every one of the individuals who have 
	straightforwardly and in a roundabout way particularly our colleagues and colleagues itself, have made profitable remark recommendations on this proposition which gave us a motivation to make strides our venture.
\end{acknowledgements}

\begin{abstract}
A Whistle-blower is a person who comes forward and shares his/her knowledge on any kind of misconduct happening in his nearby surroundings.Nowadays corruption is getting gigantic at Government level in Pakistan. You never know who is indulge and at which level, going to Police or some concerned authorities is also not a wise option.So Whistle-blower, a web based platform motivates you to step ahead for the falsification in a secure way. 

The Smart Contract – An electronic contract in the Blockchain application where the trade is happening when whistle blower reports something and gets rewarded. The Police will submit both cases and evidence against any case uploaded by any whistle blower or any other police officer. Can view both cases and evidence of any region in the country.People will see all the cases up and running currently. If you have anything against any case you have to register on a whistle blower page.The Whistle-Blower instead of real name or anything they will register through a wallet number. Keeping them unknown to the police and everyone on the system. They can submit both the cases and  evidence against any case.The Agency/Judge will keep an eye on the cases and officer assigned to that case. Reward them both officer and  whistle blower for successful closing of the case in form of Cryptocurrency.
\end{abstract}

\include{chapter1/chapter1}
\include{chapter2/chapter2}
\include{chapter3/chapter3}
\include{chapter4/chapter4}
\include{chapter5/chapter5}
\include{chapter6/chapter6}
\include{conclusions/conclusions}

%\appendix
%\include{appendix1/appendix1}

\bibliographystyle{plain}
\bibliography{bib} 
\addcontentsline{toc}{chapter}{References} 

\end{document}
